%------------------------
% Resume Template
% Author : Dany Mukesha
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Dany Mukesha}} & Email: \href{mailto:danymukesha@gmail.com}{danymukesha@gmail.com}\\
  \href{https://danymukesha.github.io}{Portfolio: danymukesha.github.io} & Mobile:~+39-366-709-5692 \\
  % \href{https://github.com/danymukesha}{GitHub: ~~github.com/danymukesha} & \\
  \href{https://linkedin.com/in/dany-mukesha}{LinkedIn: linkedin.com/in/dany-mukesha} & \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Université Côte d'Azur}{Nice, France}
      {Ph.D, Bioinformatics}{Sept. 2023 -- July 2026 (Expected)}
    \resumeSubheading
      {University of Rome Tor Vergata}{Rome, Italy}
      {MSc, Bioinformatics}{March 2020 -- July 2023}
    \resumeSubheading
      {Sapienza Università di Roma}{Rome, Italy}
      {BSc, Bioinformatics}{Nov. 2016 -- Oct. 2019}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Programming Languages}{Python, R, C++, Java, Bash, SQL}
  \resumeSubItem{Bioinformatics}{Genomics, transcriptomics, metabolomics, proteomics, single-cell analysis}
  \resumeSubItem{Machine Learning (ML)}{Regression, clustering, neural networks, Gaussian processes, feature selection, PCA/ICA, random forests, Bayesian methods, cross-validation}
  \resumeSubItem{Reproducible Research}{Conda environments, GitHub workflow versioning, Jupyter notebooks, R Markdown}
  \resumeSubItem{Tools \& Platforms}{Nextflow, Snakemake, Docker, Kubernetes, Git, HPC (Slurm/PBS), Linux, AWS, Azure}
  \resumeSubItem{Databases}{PostgreSQL, MySQL, Oracle, MongoDB}
  % \resumeSubItem{Data Standards \& Modeling}{Data modeling, metadata harmonization, biomedical ontologies (application-level), FAIR data principles}
  % \resumeSubItem{Languages}{English (C2), Italian (C2), French (C2)}
  \resumeSubItem{Languages (Spoken)}{English, Italian, French}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Université Côte d'Azur}{Nice, France}
      {PhD Researcher}{Sept. 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Biomarker Discovery}{Implement ML models integrating serum metabolomics, MRI, PET, and genetic data for early Alzheimer's detection using large-scale cohorts (such as ADNI:
        % ADNI-1:
        \href{https://clinicaltrials.gov/study/NCT00106899}{NCT00106899};
        % ADNI-GO: 
        \href{https://clinicaltrials.gov/study/NCT01078636}{NCT01078636}; 
        % ADNI-2: 
        \href{https://clinicaltrials.gov/study/NCT01231971}{NCT01231971};
        % ADNI-3: 
        % \href{https://clinicaltrials.gov/study/NCT02854033}{NCT02854033}; 
        % ADNI-4: 
        % \href{https://clinicaltrials.gov/study/NCT05617014}{NCT05617014}
        etc.)}
        \resumeItem{Multi-omics Integration}{Built pipeline for analyzing metabolomic and genomic data with 90\%+ classification accuracy for differential diagnosis between AD and Lewy body dementia}
      \resumeItemListEnd
      
    \resumeSubheading
      {Accenture Spa - Catenate Group}{Rome, Italy}
      {Software Engineer}{Jan. 2021 -- Sept. 2023}
      \resumeItemListStart
        \resumeItem{Full-Stack Development}{Built Java microservices and Angular/React frontend applications for enterprise clients}
        \resumeItem{DevOps}{Implemented CI/CD pipelines with Jenkins, Docker, Kubernetes; managed LDAP and network configurations}
      \resumeItemListEnd
      
    \resumeSubheading
      {Policlinico Agostino Gemelli IRCCS}{Rome, Italy}
      {Bioinformatician}{July 2020 -- Dec. 2020}
      \resumeItemListStart
        \resumeItem{Transcriptomic Profiling}{Analyzed RNA-seq data from ependymoma tumors; results published in International Journal of Molecular Sciences}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------International Experience-----------------
\section{International Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Wayne State University}{Detroit, MI, USA (Remote)}
      {Bioinformatician}{March 2022 -- Sept. 2023}
      \resumeItemListStart
        \resumeItem{Toxicogenomics}{Performed gene expression (RNA-seq) analysis of environmental toxins on cardiovascular health}
      \resumeItemListEnd
      
    \resumeSubheading
      {The University of Manchester}{Manchester, UK (Hybrid)}
      {Bioinformatician}{Dec. 2020 -- Aug. 2021}
      \resumeItemListStart
        \resumeItem{Epigenetics \& GWAS}{Integrated epigenomic and GWAS datasets to study immune-related genetic risk architecture in Rheumatoid Arthritis}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Selected Publications}
\resumeSubHeadingListStart
  \resumeSubItem{Journal Article}{Mukesha D, Firat H, Sacco G. Integrating large-scale serum metabolomics and APOE $\varepsilon$4 genotype for non-invasive Alzheimer's detection. \textit{medRxiv}. 2025; DOI: \href{https://doi.org/10.64898/2025.12.29.25343146}{10.64898/2025.12.29.25343146}}
  \resumeSubItem{Journal Article}{Mukesha D, Sarter M, Dubray M, et al. Targeted serum metabolomic profiling and machine learning in Alzheimer's disease using ADDIA cohort. \textit{J Alzheimers Dis}. 2025; DOI: \href{https://doi.org/10.1177/13872877251378653}{10.1177/13872877251378653}}
  \resumeSubItem{Conference}{Mukesha D, et al. Metabolomic signatures and ML models for distinguishing AD and dementia with Lewy bodies. \textit{AAIC}. 2025; DOI: \href{https://doi.org/10.1002/alz70863_110610}{10.1002/alz70863\_110610}}
  \resumeSubItem{Book}{Mukesha D. \textit{R for Proteomics}: From QC to functional analysis. 2025. \href{https://lodiag-holocron.github.io/r4proteomics/}{Online}}
  \resumeSubItem{Software}{Mukesha D. Scalable Genetic Algorithm Framework for High-Throughput Genomic Data. Zenodo. 2024}
\resumeSubHeadingListEnd

%-----------CONFERENCES & AWARDS-----------------
\section{Conferences \& Awards}
\resumeSubHeadingListStart
  \resumeSubItem{AD/PD 2026}{Talk: Biofluid biomarkers differentiating Alzheimer's from Lewy body dementia. Copenhagen, Denmark}
  \resumeSubItem{AAIC 2025}{Poster presentation. Toronto, Canada}
  \resumeSubItem{AD/PD 2025}{Poster presentation. Vienna, Austria}
  \resumeSubItem{Marie Curie PhD Scholarship}{EU Horizon 2020 (2023--2026)}
  \resumeSubItem{LazioDisco Scholarship}{Academic merit scholarship (2016--2022)}
\resumeSubHeadingListEnd

% \pagestyle{fancy}
% \fancyhf{}
% \fancyfoot[R]{\footnotesize CV -- Last updated: 13 February 2026}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}


\end{document}